|

### 2024-04-25 Drafts/Paper_1/01-analysis_no_age_correction.Rmd
I haven't updated in a while update
Working on Methods, Results, Discussion. Doing one last big run on the doubling time estimates.  Miles to go...

if(load.results==F)
{
  Stocks <- ASR_long %>%
                      dplyr::filter(!is.na(value)) %>%
                      dplyr::group_by(Stock, type) %>%
                      dplyr::summarize(count=length(unique(value))) %>%
                      dplyr::group_by(Stock) %>%
                      dplyr::summarize(types=length(unique(type))) %>%
                      dplyr::filter(types==5) %>%
                      dplyr::select(Stock)

  ASR_stocks <- ASR_long %>%
                          dplyr::filter(Stock %in% Stocks$Stock) %>%
                          dplyr::filter(!is.na(value)) %>%
                          dplyr::arrange(Stock, Year, type, as.numeric(age))

@@

  # Going to remove Sebastes norvegicus because we can't get fecundity as the only data we have is total numbers.
  #Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
  # Esmarki doesn't work great as it is assessed using a quarterly model.
  #Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]
  #i = 'ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus'
  years.tmp <- NULL
  pnm.tmp <- NULL
  waa.tmp <- NULL
  ages.tmp <- NULL
  rem.tmp <- NULL
  mx.tmp <- NULL
  NE.tmp <- NULL
  vpa.tmp <- NULL
  am.tmp <- NULL
  mr.tmp <- NULL
  abund.tmp <- NULL
  full.abund.tmp <- NULL
  full.rem.tmp <- NULL
  fs.tmp <- NULL
  for(i in Stocks)
  {
  print(i)
  ASR_sub <- ASR_long %>%
    dplyr::select(Year, Stock, type, age, value) %>%
    dplyr::filter(Stock==i)

    # Dropping the first 7 years as the 8 year olds are all missing
  if(i == "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus") ASR_sub <- ASR_sub |> collapse::fsubset(Year >= 1972)
  # maxage <- max(as.numeric(ASR_sub$age[!is.na(ASR_sub$value)]))
  # maxYear <- max(ASR_sub$Year[!is.na(ASR_sub$value)])
  # minYear <- min(ASR_sub$Year[!is.na(ASR_sub$value)])
  # forplot <- ASR_sub[as.numeric(ASR_sub$age) < (maxage+1) & ASR_sub$Year %in% minYear:maxYear,]
  # 
  # # summary plots
  # print(ggplot() + geom_line(data=forplot, aes(Year, value)) + facet_grid(type~as.numeric(age), scales="free_y") +
  #         geom_vline(data=forplot[is.na(forplot$value),], aes(xintercept=Year), colour="red") + facet_grid(type~as.numeric(age), scales="free_y") +
  #         theme_bw() + 
  #         ggtitle(i)
  # )

  age.mat <- ASR_sub %>% dplyr::filter(type=="AM") %>% dplyr::rename(AM=value) %>% dplyr::select(-type)
  # All of the age at maturities are NA in 0 and 1 year olds, so make them 0's, do that carefully just
  # in case that changes later...
  am.0s <- length(which((!is.na(age.mat$AM[age.mat$age ==0]))))
  am.1s <- length(which((!is.na(age.mat$AM[age.mat$age ==1]))))
  am.2s <- length(which((!is.na(age.mat$AM[age.mat$age ==2]))))
  if(am.0s == 0) age.mat$AM[age.mat$age ==0] <- 0
  if(am.1s == 0) age.mat$AM[age.mat$age ==1] <- 0
  if(am.2s == 0) age.mat$AM[age.mat$age ==2] <- 0

  #if(am.1s | am.0s | am.2s > 0) print("Stop, you need to check the age at maturity for either age 0 or 1 as there is data in there.")
  nat.mort <-  ASR_sub %>% dplyr::filter(type=="NM") %>% dplyr::rename(NM=value) %>% dplyr::select(-type)
  abund <- ASR_sub %>% dplyr::filter(type=="Num") %>% dplyr::rename(Num=value) %>% dplyr::select(-type)
  weight.age <- ASR_sub %>% dplyr::filter(type=="WA") %>% dplyr::rename(WA=value) %>% dplyr::select(-type)
  if(i == Stocks[30]) weight.age$WA <- weight.age$WA/1000
  removals <- ASR_sub %>% dplyr::filter(type=="Catch") %>% dplyr::rename(Catch=value) %>% dplyr::select(-type)

@@

  data <- age.mat %>%
    full_join(nat.mort) %>%
    full_join(abund) %>%
    full_join(weight.age) %>%
    full_join(removals)

@@

  rem <- data %>% dplyr::group_by(Year,.drop=F) %>% dplyr::summarize(rem=sum(Catch,na.rm=T)) #%>% dplyr::pull(rem)

  missing_rem<- NULL
  if(any(is.na(rem$rem))) 
  {
    missing_rem <- unique(data$Year)[which(is.na(rem$rem))]
    rem$rem[is.na(rem$rem)] <- median(rem$rem, na.rm=T)
  }

  #rowSums(removals[,-which(names(removals) %in% c("Year", "Stock", "type"))], na.rm=T)
  years <- data %>% dplyr::pull(Year) %>% unique() %>% sort()

  N.end <- sum(data[data$Year==max(years),]$Num)
  vpa.abund <- data %>% dplyr::group_by(Year) %>% dplyr::summarize(vpa=sum(Num,na.rm=T)) %>% pull(vpa)

  # The real mx matrix, recruits produced per individual in each age class... Not perfect as I need to offset recruits/ssb, but close enough for the moment..
  #minage
  minage <- min(as.numeric(data$age))
  #maxage
  maxage <- max(as.numeric(data$age))
  #recruits
  annual <- data.frame(Year=data$Year[data$age==minage], recruits=data$Num[data$age==minage])
  #ssn
  data$ssn <- data$Num * data$AM
  #ssb
  data$ssb <- data$ssn * data$WA #I need to figure out how to line this up with the number of recruits for the right years in the data object.... got it right for the overall r.p.ssb below.
  #tot.ssb
  annual <- data %>% group_by(Year) %>% summarize(tot.ssb = sum(ssb)) %>% left_join(annual)

  #tst <- data %>% group_by(Year) %>% summarize(tot.ssn = sum(ssn)) %>% left_join(annual)

  #r.p.ssb This needs to be offset by the age of recruits
  annual$r.p.ssb <- c(rep(NA,minage),annual$recruits[(minage+1):nrow(annual)]/annual$tot.ssb[1:(nrow(annual)-minage)])
  # recs.per.age
  data <- left_join(data, annual)
  # So I need to make an offset SSB in the 'data' object to line up with the correct r.p.ssb field.  This is probably gonna suck...
  tmp <- NULL
  for(j in 1:length(years))
  {
    tst <- data %>% dplyr::filter(Year == years[j]) %>% dplyr::select(ssb,ssn,Year,age)
    tst$Year <- tst$Year + minage
    names(tst) <- c("ssb.offset","ssn.offset","Year","age")
    tmp[[j]] <- tst
  }
  # Unpack the list
  ssb.off <- do.call('rbind',tmp)
  # And merge it with the data object
  data <- left_join(data,ssb.off,by=c("Year","age"))
  data$recs.per.age <- data$ssb.offset*data$r.p.ssb
  # mx
  # Some of the stocks are just the males and females, so these are already half the population.  Probably can just not include the male stocks in the end.
  # No longer dividing by 2 because we should really divide recruits and ssn by 2 to be female only, but that's pointless so we roll along with this.
  data$mx <- data$recs.per.age/data$ssn.offset # if(grepl("males",i)) 
  #if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn.offset/2 # Moms only! 
  data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
  # Easier to remove the years where we don't have recs.per.age...
  #data <- data %>% dplyr::filter(Year %in% years[(minage+1):length(years)])
  # Something is wrong with the decline rate method, but the exponential and logistic are working pretty... pretty... pretty good...

  age.mat <- data %>% dplyr::select("Year", "age", "AM") %>% pivot_wider(names_from=age, values_from = AM) %>% dplyr::select(-Year)
  prop.nat.mort <- data %>% dplyr::select("Year", "age", "prop.nat.mort") %>% 
                            pivot_wider(names_from=age, values_from = prop.nat.mort) %>% 
                            dplyr::select(-Year) %>% as.data.frame

  weight.age <- data %>% dplyr::select("Year", "age", "WA") %>% pivot_wider(names_from=age, values_from = WA) %>% dplyr::select(-Year)
  mx <- data %>% dplyr::select("Year", "age", "mx") %>% 
                 pivot_wider(names_from=age, values_from = mx) %>% 
                 dplyr::select(-Year) %>% as.data.frame()
  # Get the abundance matrix
  abund.age <- data %>% dplyr::select("Year", "age", "Num") %>% 
                        pivot_wider(names_from=age, values_from = Num) %>% 
                        dplyr::select(-Year) %>% as.data.frame()

@@

  full.rems <- data %>% dplyr::select("Year", "age", "Catch") %>% pivot_wider(names_from=age, values_from = Catch) %>% dplyr::select(-Year)
  full.Fs <-  data %>% dplyr::select("Year", "age", "Fs") %>% pivot_wider(names_from=age, values_from = Fs) %>% dplyr::select(-Year)

@@

  # For the years of mx without SSB info to inform them
  if(minage >0 ) 
  {
    mx.fill <- as.data.frame(matrix(rep(colMeans(mx,na.rm=T),minage),nrow=minage,byrow=T),colnames = names(mx))
    names(mx) <- names(mx.fill)
   # mx <- rbind(mx[(minage+1):nrow(mx),],mx.fill) # or is it
    mx <- rbind(mx.fill,mx[(minage+1):nrow(mx),]) # I think this is right!
  }

    years.tmp[[i]] <- years
    pnm.tmp[[i]] <- prop.nat.mort
    waa.tmp[[i]] <- weight.age
    ages.tmp[[i]] <- minage:maxage
    rem.tmp[[i]] <- rem
    mx.tmp[[i]] <- mx
    NE.tmp[[i]] <- N.end
    vpa.tmp[[i]] <- vpa.abund
    am.tmp[[i]] <- age.mat
    mr.tmp[[i]] <- missing_rem
    abund.tmp[[i]] <- abund.age
    fs.tmp[[i]] <- full.Fs
    full.rem.tmp[[i]] <- full.rems
  } #end input data loop

  save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,mr.tmp,
       am.tmp,Stocks,ASR_stocks,ASR_long,abund.tmp,fs.tmp,full.rem.tmp,
       file =  paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))

@@

  for.tune.all.res <- NULL
  for.tune.summary <- NULL
  for(i in Stocks)
  {
    years <- years.tmp[[i]]
    prop.nat.mort <- pnm.tmp[[i]] 
    #rem <- rem.tmp[[i]] 
    mx <- mx.tmp[[i]] 
    N.end <- NE.tmp[[i]] 
    ages <- ages.tmp[[i]]
    vpa.abund <- vpa.tmp[[i]] 
    abund <- abund.tmp[[i]]
    fs <-fs.tmp[[i]]
    full.rem <- rem.tmp[[i]]
    #full.abund <- full.abund.tmp[[i]]
    #all.abund <- full.abund.tmp[[i]]
    #N.end <- vpa.abund[length(vpa.abund)]
    #Pick your step size
    ss.size <- 0.01
    sensistive.stocks <- c("AFSC_GOA_Theragra_chalcogramma",
                            "DFO_2J3KL_Gadus_morhua",
                            "DFO_3Pn-4RS_Gadus_morhua",
                            "DFO_4T-4VN_Gadus_morhua",
                            "DFO_4T_Scomber_scombrus",
                            "ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus",
                            "ICES-AFWG_NEA1-2_Gadus_morhua",
                            "ICES-HAWG_NS_Ammodytes_dubius",
                            "ICES-NWWG_FA5b_Pollachius_virens",
                            "ICES-NWWG_FAPL5b1_Gadus_morhua",
                            "ICES-WGBFAS_BS 22-32_Sprattus_sprattus",
                            "ICES-WGCSE_IS7a_Gadus_morhua",
                            "ICES-WGCSE_CS7a_Merlangius_merlangus",
                            "ICES-WGCSE_CS7e-k_Gadus_morhua",
                            "ICES-WGCSE_CS27.6a_Merlangius_merlangus",
                            "ICES-WGHANSA_SP8abd_Sardina _pilchardus", 
                            "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua",
                            "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus",
                            "ICES-WGNSSK_NS 4-7d_Merlangius_merlangus",
                            "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii",
                            "NEFSC-GARMIII_SNE- MA_Limanda_ferruginea",
                            "NEFSC-GARMIII_MA_Paralichthys_dentatus",
                            "NEFSC-GARMIII_5Y_Melanogrammus_Aeglefinus")

@@

     for.tune.all.res[[i]] <- fast.for.tune
     for.tune.tmp <- data.frame(fast.for.tune$res,Stock = i)
     for.tune.summary[[i]] <- for.tune.tmp

  }

@@

  #  A quick way to get the other potentially interesting info for the stock...
  drop <- which(names(ASR_long) %in% c("Year","type","age","value"))
  meta <- NULL
  for(i in Stocks) 
  {
    meta[[i]] <- ASR_long[ASR_long$Stock == i,-drop][1,]
    meta[[i]]$age.min <- min(ages.tmp[[i]])
    meta[[i]]$age.max <- max(ages.tmp[[i]])
  }
  meta <- do.call('rbind',meta)

@@

  # Doubling time, no fishing
  dt.res <- NULL
  n.dt.sims <- 2000 # Number of simulations...
  n.years <- 100
  for(i in Stocks)
  {
    try <- for.tunes %>% dplyr::filter(Stock == i)
    meta.tmp <- meta.sub %>% dplyr::filter(Stock == i)
    double.time <- NA
    pop <- 1000
    tmp.res <- NULL
  for(s in 1:n.dt.sims)
  {
    tmp <- rep(0,n.years)

    for(y in 2:n.years)
    {
      lambda <- sample(na.omit(try$lambda),size=1)
      pop[y] <- lambda*pop[y-1]
      if(pop[y] >= 2*pop[1] & tmp[y] == 0) tmp[y:n.years] <- 1
    } # end the years loop
    tmp.res[[s]] <- data.frame(year =1:100,doubled = tmp,sim=s)
    } # end sim loop
    res.tmp <- do.call("rbind",tmp.res)

  dt.res[[i]] <- data.frame(res.tmp,meta.tmp)

  } # end Stocks loop

@@

  dub.time.summary <- dub.time %>% dplyr::group_by(Stock,year)  %>% dplyr::summarise(prop = sum(doubled)/n.dt.sims)
  dub.time.summary <- left_join(dub.time.summary,meta.sub,by="Stock")

@@

  # Do a years loop to get lambda with no fishing for each year, rather than by cohort...
    for(yy in 1:n.years)
    {
      nm <- as.numeric(tst$nm.opt[yy,])
      z <- as.numeric(tst$z.opt[yy,])
      fec <- as.numeric(tst$fecund.opt[yy,])
      nm.init <- as.numeric(tst$nm.org[yy,])
      fec.init <- as.numeric(tst$fecund.org[yy,])
      z.init <- as.numeric(tst$z.org[yy,])
      lam.no.fish <- exp(simple.lotka.r(mort = nm,fecund = fec,ages=ages)$res$r)
      lam.fish <- exp(simple.lotka.r(mort = z,fecund = fec,ages=ages)$res$r)
      lam.org.no.fish <- exp(simple.lotka.r(mort = nm.init,fecund = fec.init,ages=ages)$res$r)
      lam.org.fish <- exp(simple.lotka.r(mort =  z.init,fecund = fec.init,ages=ages)$res$r)

@@

# Other figures....

>>>>

if(load.results==F)
{
  Stocks <- ASR.long |> 
                      collapse::fsubset(!is.na(value)) |>
                      collapse::fgroup_by(Stock, type) |>
                      collapse::fsummarize(count=length(unique(value))) |>
                      collapse::fgroup_by(Stock) |>
                      collapse::fsummarize(types=length(unique(type))) |>
                      collapse::fsubset(types==5) |>
                      collapse::fselect(Stock)

  ASR.tmp <- ASR.long 
  ASR.tmp$age <- as.numeric(ASR.tmp$age)
  ASR.stocks <- ASR.tmp |> 
                          collapse::fsubset(Stock %in% Stocks$Stock) |>
                          collapse::fsubset(!is.na(value)) |>
                          collapse::roworder(Stock, Year, type, age)

@@

  # Going to remove Sebastes norvegicus because we can't get fecundity as the only data we have is total numbers.
  #Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
  # Esmarki doesn't work great as it is assessed using a quarterly model.
  #Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]
  #i = 'ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus'
  years.tmp <- NULL
  pnm.tmp <- NULL
  waa.tmp <- NULL
  ages.tmp <- NULL
  rem.tmp <- NULL
  mx.tmp <- NULL
  NE.tmp <- NULL
  vpa.tmp <- NULL
  am.tmp <- NULL
  #mr.tmp <- NULL
  abund.tmp <- NULL
  full.abund.tmp <- NULL
  full.rem.tmp <- NULL
  fs.tmp <- NULL
  for(i in Stocks)
  {
  print(i)
  ASR.sub <- ASR.long |>
    collapse::fselect(Year, Stock, type, age, value) |>
    collapse::fsubset(Stock==i)

    # Dropping the first 7 years as the 8 year olds are all missing
  if(i == "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus") ASR.sub <- ASR.sub |> collapse::fsubset(Year >= 1972)
  # maxage <- max(as.numeric(ASR.sub$age[!is.na(ASR.sub$value)]))
  # maxYear <- max(ASR.sub$Year[!is.na(ASR.sub$value)])
  # minYear <- min(ASR.sub$Year[!is.na(ASR.sub$value)])
  # forplot <- ASR.sub[as.numeric(ASR.sub$age) < (maxage+1) & ASR.sub$Year %in% minYear:maxYear,]
  # 
  # # summary plots
  # print(ggplot() + geom_line(data=forplot, aes(Year, value)) + facet_grid(type~as.numeric(age), scales="free_y") +
  #         geom_vline(data=forplot[is.na(forplot$value),], aes(xintercept=Year), colour="red") + facet_grid(type~as.numeric(age), scales="free_y") +
  #         theme_bw() + 
  #         ggtitle(i)
  # )

  age.mat <- ASR.sub |> collapse::fsubset(type=="AM") |> dplyr::rename(AM=value) |> collapse::fselect(-type)
  # All of the age at maturities are NA in 0 and 1 year olds, so make them 0's, do that carefully just
  # in case that changes later...
  am.0s <- length(which((!is.na(age.mat$AM[age.mat$age ==0]))))
  am.1s <- length(which((!is.na(age.mat$AM[age.mat$age ==1]))))
  am.2s <- length(which((!is.na(age.mat$AM[age.mat$age ==2]))))
  if(am.0s == 0) age.mat$AM[age.mat$age ==0] <- 0
  if(am.1s == 0) age.mat$AM[age.mat$age ==1] <- 0
  if(am.2s == 0) age.mat$AM[age.mat$age ==2] <- 0

  #if(am.1s | am.0s | am.2s > 0) print("Stop, you need to check the age at maturity for either age 0 or 1 as there is data in there.")
  nat.mort <-  ASR.sub |> collapse::fsubset(type=="NM") |> dplyr::rename(NM=value) |> collapse::fselect(-type)
  abund <- ASR.sub |> collapse::fsubset(type=="Num") |> dplyr::rename(Num=value) |> collapse::fselect(-type)
  weight.age <- ASR.sub |> collapse::fsubset(type=="WA") |> dplyr::rename(WA=value) |> collapse::fselect(-type)
  if(i == Stocks[30]) weight.age$WA <- weight.age$WA/1000
  removals <- ASR.sub |> collapse::fsubset(type=="Catch") |> dplyr::rename(Catch=value) |> collapse::fselect(-type)

@@

  data <- age.mat |>
    full_join(nat.mort) |>
    full_join(abund) |>
    full_join(weight.age) |>
    full_join(removals)

@@

  rem <- data |> collapse::fgroup_by(Year) |> collapse::fsummarize(rem=sum(Catch,na.rm=T)) #|> dplyr::pull(rem)
  #rem <- data |> dplyr::group_by(Year,.drop=F) |> collapse::fsummarize(rem=sum(Catch,na.rm=T)) #|> dplyr::pull(rem)

  # Never run, so not doing anything.
  # missing_rem<- NULL
  # if(any(is.na(rem$rem))) 
  # {
  #   missing_rem <- unique(data$Year)[which(is.na(rem$rem))]
  #   rem$rem[is.na(rem$rem)] <- median(rem$rem, na.rm=T)
  # }

  #rowSums(removals[,-which(names(removals) %in% c("Year", "Stock", "type"))], na.rm=T)
  years <- data |> dplyr::pull(Year) |> unique() |> sort()

  N.end <- sum(data[data$Year==max(years),]$Num)
  vpa.abund <- data |> dplyr::group_by(Year) |> dplyr::summarize(vpa=sum(Num,na.rm=T)) |> pull(vpa)

  # The real mx matrix, recruits produced per individual in each age class... Not perfect as I need to offset recruits/ssb, but close enough for the moment..
  #minage
  minage <- min(as.numeric(data$age))
  #maxage
  maxage <- max(as.numeric(data$age))
  #recruits
  annual <- data.frame(Year=data$Year[data$age==minage], recruits=data$Num[data$age==minage])
  #ssn
  data$ssn <- data$Num * data$AM
  #ssb
  data$ssb <- data$ssn * data$WA #I need to figure out how to line this up with the number of recruits for the right years in the data object.... got it right for the overall r.p.ssb below.
  #tot.ssb
  annual <- data |> group_by(Year) |> summarize(tot.ssb = sum(ssb)) |> left_join(annual)

  #tst <- data |> group_by(Year) |> summarize(tot.ssn = sum(ssn)) |> left_join(annual)

  #r.p.ssb This needs to be offset by the age of recruits. So here's my lining this up logic.  For age 0, we get
  # the recruit and SSB estimates from the same survey, thus these age 0 recruits will have been produced by the SSB in the previous year...
  # So the R in 1970 were produced by SSB in 1969 when min age =0
  # If min.age = 1 then R in 1970 is produced by SSB in 1968... and so on.
  # FIX 1 "Recruit year" = SSB year + min.age + 1 (or min.age +2 as SSB.year is the first column)
  # Now for RPS there's another wrinkle because of this, because our model is N(1970) = lambda * N(1969) and lambda is made up of lx and mx
  # so if the recruits show up in 1970, the fecundity term that gets us there (irrespective of the age offset) has to be for 1969, becuase
  # that gets us to the babies that show up in 1970
  # FIX 2 So "RPS year, recs.per.age year, and mx year" = SSB year + min.age
  # I believe this to be correct, but we all need to discuss this to make sure the logic holds.
  annual$r.p.ssb <- c(rep(NA,minage),annual$recruits[(minage+2):nrow(annual)]/annual$tot.ssb[1:(nrow(annual)-minage-1)],NA)
  # recs.per.age
  data <- left_join(data, annual)
  # So I need to make an offset SSB in the 'data' object to line up with the correct r.p.ssb field.  This is probably gonna suck...
  tmp <- NULL
  for(j in 1:length(years))
  {
    tst <- data|> collapse::fsubset(Year == years[j]) |> collapse::fselect(ssb,ssn,Year,age)
    tst$Year <- tst$Year + minage # We want this to line up the the RPS year, so just adding minage here.
    names(tst) <- c("ssb.offset","ssn.offset","Year","age")
    tmp[[j]] <- tst
  }
  # Unpack the list
  ssb.off <- do.call('rbind',tmp)
  # And merge it with the data object
  data <- left_join(data,ssb.off,by=c("Year","age"))
  data$recs.per.age <- data$ssb.offset*data$r.p.ssb
  # mx
  # Some of the stocks are just the males and females, so these are already half the population.  Probably can just not include the male stocks in the end.
  # No longer dividing by 2 because we should really divide recruits and ssn by 2 to be female only, but that's pointless so we roll along with this.
  data$mx <- data$recs.per.age/data$ssn.offset # if(grepl("males",i)) 
  #if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn.offset/2 # Moms only! 
  data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
  # Easier to remove the years where we don't have recs.per.age...
  #data <- data |> collapse::fsubset(Year %in% years[(minage+1):length(years)])
  # Something is wrong with the decline rate method, but the exponential and logistic are working pretty... pretty... pretty good...

  age.mat <- data |> collapse::fselect("Year", "age", "AM") |> 
                     pivot_wider(names_from=age, values_from = AM) |> collapse::fselect(-Year)
  prop.nat.mort <- data |> collapse::fselect("Year", "age", "prop.nat.mort") |> 
                            pivot_wider(names_from=age, values_from = prop.nat.mort) |> 
                            collapse::fselect(-Year) |> as.data.frame()

  weight.age <- data |> collapse::fselect("Year", "age", "WA") |> pivot_wider(names_from=age, values_from = WA) |> collapse::fselect(-Year)
  mx <- data |> collapse::fselect("Year", "age", "mx") |> 
                 pivot_wider(names_from=age, values_from = mx) |> 
                 collapse::fselect(-Year) |> as.data.frame()
  # Get the abundance matrix
  abund.age <- data |> collapse::fselect("Year", "age", "Num") |> 
                        pivot_wider(names_from=age, values_from = Num) |> 
                        collapse::fselect(-Year) |> as.data.frame()

@@

  full.rems <- data |> collapse::fselect("Year", "age", "Catch") |> pivot_wider(names_from=age, values_from = Catch) |> collapse::fselect(-Year)
  full.Fs <-  data |> collapse::fselect("Year", "age", "Fs") |> pivot_wider(names_from=age, values_from = Fs) |> collapse::fselect(-Year)

@@

  # I had filled the years with no SSB data to inform them.  instead I'm going to remove those years...

   if(minage >0) 
  {
    rm <- -(1:minage)
    years <- years[rm]
    prop.nat.mort <- prop.nat.mort[rm,]
    weight.age <- weight.age[rm,]
    rem <- rem[rm,]
    mx <- mx[rm,]
    vpa.abund <- vpa.abund[rm]
    age.mat <- age.mat[rm,]
    abund.age <- abund.age[rm,]
    full.Fs <- full.Fs[rm,]
    full.rems <- full.rems[rm,]
   }
  #   mx.fill <- as.data.frame(matrix(rep(colMeans(mx,na.rm=T),minage),nrow=minage,byrow=T),colnames = names(mx))
  #   names(mx) <- names(mx.fill)
  #  # mx <- rbind(mx[(minage+1):nrow(mx),],mx.fill) # or is it
  #   mx <- rbind(mx.fill,mx[(minage+1):nrow(mx),]) # I think this is right!
  # }

    years.tmp[[i]] <- years
    pnm.tmp[[i]] <- prop.nat.mort
    waa.tmp[[i]] <- weight.age
    ages.tmp[[i]] <- minage:maxage
    rem.tmp[[i]] <- rem
    mx.tmp[[i]] <- mx
    NE.tmp[[i]] <- N.end
    vpa.tmp[[i]] <- vpa.abund
    am.tmp[[i]] <- age.mat
    #mr.tmp[[i]] <- missing_rem
    abund.tmp[[i]] <- abund.age
    fs.tmp[[i]] <- full.Fs
    full.rem.tmp[[i]] <- full.rems
  } #end input data loop

  save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,mr.tmp,
       am.tmp,Stocks,ASR.stocks,ASR.long,abund.tmp,fs.tmp,full.rem.tmp,
       file =  paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))

@@

  for.tune.all.res <- NULL
  for.tune.summary <- NULL
  for(i in Stocks)
  {
    years <- years.tmp[[i]]
    prop.nat.mort <- pnm.tmp[[i]] 
    #rem <- rem.tmp[[i]] 
    mx <- mx.tmp[[i]] 
    N.end <- NE.tmp[[i]] 
    ages <- ages.tmp[[i]]
    vpa.abund <- vpa.tmp[[i]] 
    abund <- abund.tmp[[i]]
    fs <-fs.tmp[[i]]
    full.rem <- rem.tmp[[i]]
    #full.abund <- full.abund.tmp[[i]]
    #all.abund <- full.abund.tmp[[i]]
    #N.end <- vpa.abund[length(vpa.abund)]
    #Pick your step size
    ss.size <- 0.005
    sensistive.stocks <- c("AFSC_GOA_Theragra_chalcogramma",
                            "DFO_2J3KL_Gadus_morhua",
                            "DFO_3Pn-4RS_Gadus_morhua",
                            "DFO_4T-4VN_Gadus_morhua",
                            "DFO_4T_Scomber_scombrus",
                            "ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus",
                            "ICES-AFWG_NEA1-2_Gadus_morhua",
                            "ICES-HAWG_NS_Ammodytes_dubius",
                            "ICES-NWWG_FA5b_Pollachius_virens",
                            "ICES-NWWG_FAPL5b1_Gadus_morhua",
                            "ICES-WGBFAS_BS 22-32_Sprattus_sprattus",
                            "ICES-WGCSE_IS7a_Gadus_morhua",
                            "ICES-WGCSE_CS7a_Merlangius_merlangus",
                            "ICES-WGCSE_CS7e-k_Gadus_morhua",
                            "ICES-WGCSE_CS27.6a_Merlangius_merlangus",
                            "ICES-WGHANSA_SP8abd_Sardina _pilchardus", 
                            "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua",
                            "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus",
                            "ICES-WGNSSK_NS 4-7d_Merlangius_merlangus",
                            "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii",
                            "NEFSC-GARMIII_SNE- MA_Limanda_ferruginea",
                            "NEFSC-GARMIII_MA_Paralichthys_dentatus",
                            "NEFSC-GARMIII_5Y_Melanogrammus_Aeglefinus",
                            "NEFSC_NWA_Scomber _scombrus")

@@

     for.tune.all.res[[i]] <- fast.for.tune
     for.tune.tmp <- data.frame(fast.for.tune$res,Stock = i)
     for.tune.summary[[i]] <- for.tune.tmp
  }

@@

  #  A quick way to get the other potentially interesting info for the stock...
  drop <- which(names(ASR.long) %in% c("Year","type","age","value"))
  meta <- NULL
  for(i in Stocks) 
  {
    meta[[i]] <- ASR.long[ASR.long$Stock == i,-drop][1,]
    meta[[i]]$age.min <- min(ages.tmp[[i]])
    meta[[i]]$age.max <- max(ages.tmp[[i]])
  }
  meta <- do.call('rbind',meta)

@@

  # Doubling time, no fishing
  dt.res <- NULL
  n.dt.sims <- 1000 # Increase to 1000 for final run, which takes like a full day or something 
  n.years <- 100
  for(i in Stocks)
  {
    str.time <- Sys.time()
    try <- for.tune.all[[i]]
    meta.tmp <- try$meta
    age.4.sim <- meta.tmp$age.min:meta.tmp$age.max
    double.time <- NA
    pop <- 1000
    tmp.res <- NULL
  for(s in 1:n.dt.sims)
  {

    tmp <- rep(0,n.years)
    for(y in 2:n.years)
    {

      # Get our sample for this run
      f.pick <- sample(nrow(try$fecund.opt),size=1)
      nm.pick <- sample(nrow(try$nm.opt),size=1)
      fec.samp <- try$fecund.opt[f.pick,]
      # This is instantaneous rate, which is what the Lotka function is expected (it is set up expecting instantaneous)
      nm.samp <- try$nm.opt[nm.pick,] 
      # now put these into Euler-lotka to get an r estimate
      res <- simple.lotka.r(mort = nm.samp,fecund=fec.samp,ages=age.4.sim)
      r.val <- res$res$r
      # If r is > 5 (lambda = exp(5)) it generally means the simple.lotka didn't converge (bad combo of fec and nm)
      # So we'll need to resample them until it is < 5
      while(r.val >= 5)
      {
        print("Resampling due to bat shit r value")
        f.pick <- sample(nrow(try$fecund.opt),size=1)
        nm.pick <- sample(nrow(try$nm.opt),size=1)
        fec.samp <- try$fecund.opt[f.pick,]
        # This is instantaneous rate, which is what the Lotka function is expected (it is set up expecting instantaneous)
        nm.samp <- try$nm.opt[nm.pick,] 
        # now put these into Euler-lotka to get an r estimate
        res <- simple.lotka.r(mort = nm.samp,fecund=fec.samp,ages=age.4.sim)
        r.val <- res$res$r
      } # end while loop
      pop[y] <- exp(r.val)*pop[y-1]
      if(pop[y] >= 2*pop[1] & tmp[y] == 0) tmp[y:n.years] <- 1
    } # end the years loop
    tmp.res[[s]] <- data.frame(year =1:n.years,doubled = tmp,sim=s)

    } # end sim loop
    res.tmp <- do.call("rbind",tmp.res)

  dt.res[[i]] <- data.frame(res.tmp,meta.tmp)
  count <- 0
  print(paste0("Stock ",i," Sim ", s," time =", round(Sys.time()-str.time,digits=1)," minutes Stock number",count+1))
  } # end Stocks loop

@@

  dub.time.summary <- dub.time |> collapse::fgroup_by(Stock,year)  |> collapse::fsummarise(prop = sum(doubled)/n.dt.sims)
  dub.time.summary <- left_join(dub.time.summary,meta.sub,by="Stock")

@@

  # Do a years loop to get lambda with no fishing for each year, rather than by cohort...
    for(yy in 1:(n.years-1))
    {
      nm <- as.numeric(tst$nm.opt[yy,])
      z <- as.numeric(tst$z.opt[yy,])
      fec <- as.numeric(tst$fecund.opt[yy,])
      nm.init <- as.numeric(tst$nm.org[yy,])
      fec.init <- as.numeric(tst$fecund.org[yy,])
      z.init <- as.numeric(tst$z.org[yy,])
      lam.no.fish <- exp(simple.lotka.r(mort = nm,fecund = fec,ages=ages)$res$r)
      lam.fish <- exp(simple.lotka.r(mort = z,fecund = fec,ages=ages)$res$r)
      lam.org.no.fish <- exp(simple.lotka.r(mort = nm.init,fecund = fec.init,ages=ages)$res$r)
      lam.org.fish <- exp(simple.lotka.r(mort =  z.init,fecund = fec.init,ages=ages)$res$r)

@@

# FIX: A density dependence figure, this isn't perfect as the lambda's aren't quiet lined up right because of recruitment offset
# That said, recruitment in these cases also integrates all processes that happens from birth-recruitment
# So maybe it is kinda reasonable?
#
